FraCaS: Temporal Analysis

### 2020-10-27 paper2020/paper.tex
minor additions

Unicity of action plays the role of event coreference in
(neo-)davidsonian account \todo{stergios: citation}. It is also a fine-grained
principle, allowing coreference to take into account certain arguments
when referencing. As we detail below, taking arguments into account
yields is critical to handle repeatability of achievements.

@@

We treat verbs in the progressive form as different semantically from
the non-progressive form. For example, ``John was writing a book'' is
encoded as
$∃(t_1, t_2). t_1≤ t_2, t_2 ≤ now, PROG\_write(John,book,t_1,t_2)$,
while ``John wrote a book'' is encoded as
$∃(t_1, t_2). t_1≤ t_2, t_2 ≤ now, write(John,book,t_1,t_2)$. This is
necessary, because $PROG\_write$ is subject to
$\constant{subsumption}$: if John is writing in the interval
$[t_1,t_2]$ then he is writing in any sub-interval of
$[t_1,t_2]$. However, the same cannot be said of $write$: the
end-points of the interval indicate the time needed to complete the
achievement. (For example, ``John wrote a book in 1993'' neither
entails ``John wrote a book in January 1993'' nor ``John wrote a book
in December 1993''.) In fact, \emph{write}, in the non-progressive
from, is on the contrary subject to $\constant{unicity}$. Finally, we
also have $write(x,y,t_1,t_2) → PROG\_write(x,y,t_1,t_2)$. That is,
the achievement (or \emph{activity} in our terminology) variant implies the stative variant, in the
same interval.  Consequently we get the entailment from ``John wrote a
book'' to ``John was writing a book''.

>>>>

Unicity of action plays the role of event coreference in
(neo-)Davidsonian accounts \citep{parsons1990events}. It is also a fine-grained
principle, allowing coreference to take into account certain arguments
when referencing. As we detail below, taking arguments into account
yields is critical to handle repeatability of achievements.

@@

We treat verbs in the progressive form as different semantically from
the non-progressive form. For example, ``John was writing a book'' is
encoded as
$∃(t_1, t_2). t_1≤ t_2, t_2 ≤ now, PROG\_write(John,book,t_1,t_2)$,
while ``John wrote a book'' is encoded as
$∃(t_1, t_2). t_1≤ t_2, t_2 ≤ now, write(John,book,t_1,t_2)$. This is
necessary, because $PROG\_write$ is subject to
$\constant{subsumption}$: if John is writing in the interval
$[t_1,t_2]$ then he is writing in any sub-interval of
$[t_1,t_2]$. However, the same cannot be said of $write$: the
end-points of the interval indicate the time needed to complete the
achievement. (For example, ``John wrote a book in 1993'' neither
entails ``John wrote a book in January 1993'' nor ``John wrote a book
in December 1993''.) In fact, \emph{write}, in the non-progressive
from, is on the contrary subject to $\constant{unicity}$. Finally, we
also have $write(x,y,t_1,t_2) → PROG\_write(x,y,t_1,t_2)$. That is,
the achievement (or \emph{activity} in our terminology) variant implies the stative variant, in the
same interval.  Consequently we get the entailment from ``John wrote a
book'' to ``John was writing a book''.\footnote{Note that this is a different interpretation of the usual accounts of the progressive in the literature which take a progressive sentence  to be  true at an interval $t_0$
 iff there is an interval $t_1$ such that $t_0$ is a non final
subinterval of $t_1$ and the progressiver sentence is true at $t_1$ \citep{ogihara2007tense}. In terms of implementation, the solution we provide here seems to be simpler.}
